Timely Object Detection

### 2012-02-15 writeups/eccv12/eccv12.tex
updated schedule

\subsection{Reward} \label{sec:reward}
The goal of our policy is Anytime performance, so it would be limiting to evaluate only at deadline time.
Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).
Toward this goal, we formulate a \emph{reward function} that encourages this behavior by assigning a score to an action taken in a belief state.

@@

\subsubsection{Information gain}
A common approach to our kind of problem is to minimize uncertainty as quickly as possible.
Specifically,

@@

\subsection{The value function} \label{sec:value}
At each step, we want to pick the action that maximizes the expected rewards until the end of the episode.
We therefore define our policy as
\begin{equation}
\argmax_{a \in \mathcal{A} \setminus \mathcal{O}} \theta^\top \phi(b,a)
\end{equation}

@@

\subsubsection{Manually specified greedy value function}

\subsubsection{Learning the greedy policy}

@@

This approach has been shown to scale to large problems in \cite{Branavan2009,Sutton2000}, although it has been proven to converge only to local maxima and only for MDPs.

>>>>

\subsection{Reward} \label{sec:reward}
The goal of our policy is Anytime performance, so it would be limiting to evaluate only at deadline time.
Optimal performance results from becoming maximally certain of the correct values $C_i$ as quickly as possible (given the setup time).
Toward this goal, we formulate a \emph{reward function} that encourages this behavior by assigning a score to a belief state.

@@

\subsubsection{Information gain}
A common approach to our kind of problem is to minimize uncertainty as quickly as possible.
Therefore we define the reward as a function of the negative residual entropy, following \cite{Gao2011}.

@@

\subsection{The value function} \label{sec:value}
At each step, we want to pick the action that maximizes the expected rewards until the end of the episode.
We therefore define our policy as
\begin{equation}
\pi(b) = \argmax_{a \in \mathcal{A} \setminus \mathcal{O}} \theta^\top \phi(b,a)
\end{equation}

@@

\subsubsection{Greedy expected-value}
We can compute the expected value of the reward function given a distribution over the classifier response.
If we define the value function by this expectation, we will have constructed a one-step greedy policy.

\note{Discuss submodularity defense of greedy policies here; costs are tricky though.}

\subsubsection{Learning the greedy policy}
We note that we can represent the one-step greedy policy value function as a scalar product

@@

This approach has been shown to scale to large problems in \cite{Branavan2009}, although it has been proven to converge only to local maxima and only for MDPs \cite{Sutton2000}.
